Demes: a standard format for demographic models

### 2022-05-18 software-table.tex
Remove stdpopsim from software table
Update dadi entry in Table 1

\dadi &
    Summary of what dadi does and how it implements Demes~\citep{gutenkunst2009inferring}.
    \ggcomment{what is the status of dadi/Demes support?}
    \\

@@

\stdpopsim &
    A community-maintained collection of empirical data for species
    and demographic models specified in Demes
    format~\citep{adrion2020community}.
    \ggcomment{stdpopsim doesn't yet have Demes support}
    \\

>>>>

\dadi &
       Simulate SFS from Demes models, infer demographic history and distributions of fitness effects~\citep{gutenkunst2009inferring}.
    \\

@@
